\vspace{-15mm} \fontsize{24pt}{10pt}\selectfont \textbf{Traversing Symmetric NAT with predictable port allocation function}

### 2013-12-10 paper.tex
algI benefits, port pool exhaustion

\section{Related work}
Some interesting algorithms for traversing symmetric NAT were proposed by Y. Takeda in \citep{takeda}, but the case both clients are behind symmetric NAT
with port sensitive allocation function is not covered. It mentions that sending more packets won't increase probability of establishing the new connection.
Our motivation is to show that it is actually possible.

@@

@@

\section{Evaluation}
ToDo;
\begin{itemize}
 \item ToDo: algorithm success rate evaluation w.r.t. $\lambda, T$, graphs, graphs, graphs, \dots
 \item ToDo: algorithm pros/cons w.r.t. system requirements, applicability
 \item ToDo: fitting model to the real data from MU network
 \item ToDo: evaluating algorithms on real data from MU network
\end{itemize}

>>>>

% \section{Related work}
Some interesting algorithms for traversing symmetric NAT were proposed by Y. Takeda in \citep{takeda}, but the case both clients are behind symmetric NAT
with port sensitive allocation function is not covered. It mentions that sending more packets won't increase probability of establishing the new connection.
Our motivation is to show that it is actually possible.

@@

\paragraph{Port pool exhaustion.} NAT timeout\footnote{Allocation is deleted if no packet is detected in this time interval} is assumed to be 3~minutes, 
what is common value in practice. This constrains $\lambda$ to the interval $[0, 0.36]$, intuitively from $0$ to $360$ new connections in $1$~s on average. 
If it is higher the NAT is rendered as unusable since the port pool is exhausted\footnote{$P[X > 65535] = 0.0019, X \sim Po(180000 \cdot 0.36)$} pretty fast.

@@

\section{Evaluation}

\paragraph{Algorithm I and II comparison.} 
Algorithm I has following benefits over II:
\begin{compactitem}
 \item works with high success rate for $\lambda \in [0, 0.035] \sim 35$ new connections in 1~s on average.
 \item can be stopped as soon as connection is established, overhead is proportional to $\lambda$.
 \item single source port is used, only one listening thread is needed to implement
it\footnote{NAT is abused to multiplex multiple connections to one source port} compared to the Alg. II.
This fact makes practical implementation simple and lightweight w.r.t. needed system resources.
 \item is $\lambda$-invariant. Provided network load is low no additional measurements are needed.
\end{compactitem}

ToDo;
\begin{itemize}
 \item ToDo: algorithm success rate evaluation w.r.t. $\lambda, T$, graphs, graphs, graphs, \dots
 \item ToDo: algorithm pros/cons w.r.t. system requirements, applicability
 \item ToDo: fitting model to the real data from MU network
 \item ToDo: evaluating algorithms on real data from MU network
\end{itemize}
